%--------------------------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%--------------------------------------------
% https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs

\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS-----------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1
%---------------------------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%------------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING-------------------------------
\begin{center}
    \textbf{\Huge \scshape Dhairya Pratap Singh Gaur} \\ \vspace{1pt}
    \small +91 7454948411 $|$ \href{mailto:dhairyagaur98@gmail.com}{{dhairyagaur98@gmail.com}}    \\ 
    \small  
    \href{https://www.linkedin.com/in/asmogaur/}{\bf LinkedIn} $|$
    \href{https://github.com/Asmogaur}{\bf GitHub} 
    
\end{center}
%-------------------------------------------------

%-----------PROJECTS------------------------------
\section{Profile}
\begin{itemize}[leftmargin=0.15in, label={}]
\item 
Data Engineer with 3+ years of experience leveraging big data technologies \textbf{(Python, SQL, PySpark, Databricks)} to build scalable \textbf{ETL} pipelines, process large datasets, and deliver actionable insights. Proven ability to streamline workflows and enhance data quality across cloud-based platforms \textbf{(GCP)}.
\end{itemize}
%------------------------------------------------

%---------TECHNICAL SKILLS-----------------------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{:\hspace{0.77cm} Python, SQL, C++} \\
     \textbf{Big Data Technologies}{:\hspace{1.20cm} Spark, PySpark, Spark SQL} \\
     \textbf{Cloud Computing}{:\hspace{1.98cm} Databricks, Google Cloud Platform (GCP)} \\
     \textbf{Data Engineering Concepts}{:\hspace{0.30cm} Data Warehouse, Data Lake, Data Lakehouse, Medallion Architecture }\\
     \textbf{Visualisation Tools}{:\hspace{1.81cm} Amazon QuickSight} \\
    }}
 \end{itemize}
%-----------------------------------------------

%-----------EXPERIENCE--------------------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KPMG}{November 2021 - Present}
      {Data Engineer}{Bangalore, India}
      \resumeItemListStart
      \resumeItem{Ported and optimised SQL scripts from Teradata for catalog tables to ensure efficient and effective migration.}
      \resumeItem{Built metadata scripts and constructed \textbf{ETL} data pipelines within the \textbf{Medallion Architecture} framework.}
      \resumeItem{Implemented data processing and transformation logic using \textbf{PySpark} and optimised queries with \textbf{Spark SQL}, reducing runtime by 50\%.}
      \resumeItem{Deployed and managed scalable data solutions leveraging \textbf{Databricks} for collaborative development and performance tuning.}
      \resumeItemListEnd

      \resumeItemListStart
      \resumeItem{Designed and implemented detailed reports and data analysis pipelines.}
      \resumeItem{Developed interactive, data-driven dashboards utilising \textbf{Amazon QuickSight} for visualisation.}
      \resumeItem {Managed database operations and optimised queries using \textbf{pgAdmin} with \textbf{PostgreSQL}.}
      \resumeItemListEnd

    \resumeSubheading
      {SmartBridge}{May 2020 - June 2020}
      {Machine Learning Engineer (Intern)}{Hyderabad, India}
      \resumeItemListStart
      \resumeItem {Developed an automated AI system to predict individual life expectancy, achieving a predictive accuracy of 93\%.}
      \resumeItem {Incorporated various factors such as demographic, health, lifestyle, and socioeconomic data.}
      \resumeItem {Utilized IBM frameworks, including :}
      \resumeItem{\textbf{IBM Cloud} for infrastructure and scalability.}
      \resumeItem{\textbf{IBM Watson} for data processing and machine learning model development.}
      \resumeItem{\textbf{IBM Machine Learning Instance} for model training, deployment, and real-time predictions.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%---------------------------------------------------

%------------CERTIFICATIONS-------------------------
\section{Certifications}
    \resumeItemListStart
    \resumeItem {Databricks Fundamentals}
    \resumeItem {Databricks Lakehouse Fundamentals}
    \resumeItem {AWS Databricks Platform Architect}
    \resumeItem {GCP Databricks Platform Architect}
    \resumeSubHeadingListEnd
%---------------------------------------------------

%-----------EDUCATION-------------------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Guru Gobind Singh Indraprastha University}{CGPA - 7.1}
      {Bachelor of Technology in Electronic and Communication Engineering}{August 2017 - July 2021}
    \resumeSubheading
      {Kendriya Vidyalaya Sangathan}{12th - 77.4\%}
      {Physics, Chemistry, Mathematics, English and Computer Science}{April 2015 - March 2016}
  \resumeSubHeadingListEnd
%---------------------------------------------------
\end{document}
