%--------------------------------------------------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%--------------------------------------------------------------------
% https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs

\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------------------------------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1
%----------------------------------------------------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%---------------------------------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING----------------------------------------------------
\begin{center}
    \textbf{\Huge \scshape Dhairya Pratap Singh Gaur} \\ \vspace{1pt}
    \small +91 7454948411 $|$ \href{mailto:dhairyagaur98@gmail.com}{{dhairyagaur98@gmail.com}}    \\ 
    \small  
    \href{https://www.linkedin.com/in/asmogaur/}{\bf LinkedIn} $|$
    \href{https://github.com/Asmogaur}{\bf GitHub} 
    
\end{center}
%--------------------------------------------------------------------

%-----------PROJECTS-------------------------------------------------
\section{Profile}
\begin{itemize}[leftmargin=0.15in, label={}]
\item 
Data Engineer with over 4+ years of experience building scalable \textbf{ETL} pipelines, big data processing, and cloud-based solutions. Proficient in \textbf{Python, SQL, PySpark, Databricks, Snowflake, and GCP}, with expertise in optimizing workflows and improving data quality. Passionate about delivering high-performance data solutions that drive business insights.
\end{itemize}
%--------------------------------------------------------------------

%---------TECHNICAL SKILLS-------------------------------------------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{:\hspace{0.76cm} Python, SQL} \\
     \textbf{Big Data Technologies}{:\hspace{1.19cm} Spark, PySpark, Spark SQL, HDFS} \\
     \textbf{Cloud Platforms}{:\hspace{2.21cm} Databricks, Snowflake, Google Cloud Platform (GCP)} \\
     \textbf{Data Engineering Concepts}{:\hspace{0.28cm} ETL, Data Warehouse, Data Lake, Data Lakehouse, Data Modelling} \\
     \textbf{Visualization Tools}{:\hspace{1.77cm} Amazon QuickSight, SIGMA} \\
     \textbf{Other Tools}{:\hspace{3.04cm} DBT, Git/Github, Airflow} \\
    }}
 \end{itemize}
%-------------------------------------------------------------------

%-----------EXPERIENCE----------------------------------------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KPMG}{November 2021 - February 2026}
      {Data Engineer}{Bangalore, India}
      \resumeItemListStart
      \resumeItem{\textbf{Client 1 (Domain - BFSI and Fintech) : Data Platform Modernization using PySpark}}
      \resumeItem{Optimized SQL scripts from Teradata for catalog tables to ensure efficient and effective migration.}
      \resumeItem{Built metadata scripts and constructed \textbf{ETL} data pipelines within the \textbf{Medallion Architecture} framework.}
      \resumeItem{Implemented data processing and transformation logic using \textbf{PySpark} and optimized queries with \textbf{Spark SQL}, reduced query runtime by \textbf{60\%}.}
      \resumeItem{Deployed and managed scalable data solutions leveraging \textbf{Databricks} for collaborative development and performance tuning.}
      \resumeItemListEnd

      \resumeItemListStart
      \resumeItem{\textbf{Client 2 (Domain - FMCG and Retail) : Data Pipeline Implementation and Analytics Development}}
      \resumeItem{Ingested data from heterogeneous source systems into the RAW layer of \textbf{Snowflake} (DEV) and developed modular business transformations in the curated layer using \textbf{dbt} and \textbf{SnowSQL}, improving data stability by \textbf{20\%}.}
      \resumeItem{Designed and deployed validated data pipelines from DEV to PROD through \textbf{GitHub} PRs, ensuring successful quality checks and seamless production releases.}
      \resumeItem {Developed BI dashboards in \textbf{SIGMA} and implemented \textbf{Row-Level Security (RLS)} to enable secure, role-based data access across stakeholders.}
      \resumeItemListEnd

    \resumeSubheading
      {SmartBridge}{May 2020 - June 2020}
      {Machine Learning Engineer (Intern)}{Hyderabad, India}
      \resumeItemListStart
      \resumeItem {Developed an automated AI system to predict individual life expectancy, achieved a predictive accuracy of \textbf{94\%}.}
      \resumeItem {Incorporated various factors such as demographic, health, lifestyle, and socioeconomic data.}
      \resumeItem{\textbf{IBM Cloud} for infrastructure and scalability.}
      \resumeItem{\textbf{IBM Watson} for data processing and machine learning model development.}
      \resumeItem{\textbf{IBM Machine Learning Instance} for model training, deployment, and real-time predictions.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%--------------------------------------------------------------------

%------------CERTIFICATIONS------------------------------------------
\section{Certifications}
    \resumeItemListStart
    \resumeItem {Databricks AWS Platform Architect}
    \resumeItem {Databricks Azure Platform Architect}
    \resumeItem {Databricks GCP Platform Architect}
    \resumeSubHeadingListEnd
%--------------------------------------------------------------------

%-----------EDUCATION------------------------------------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Guru Gobind Singh Indraprastha University}{CGPA - 7.1}
      {Bachelor of Technology in Electronics and Communications  Engineering}{August 2017 - July 2021}
    \resumeSubheading
      {Kendriya Vidyalaya Sangathan}{12th - 77.4\%}
      {Physics, Chemistry, Mathematics, English and Computer Science}{April 2015 - March 2016}
  \resumeSubHeadingListEnd
%--------------------------------------------------------------------
\end{document}
